---
title: "Map activity"
author: "Juan Flores"
date: "September 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## Map with Leaflet

This document is to present a map with some features, done using the leaflet package in R.



### Data generation

Creating random statistics about health (sick people) for 6 states in the United States.

```{r creating random health data}

StatesHealth <- data.frame(
  State = c("New York","California","Texas","Washington","Illinois","Georgia"),
  Population = c(8538000,39250000,27860000,7288000,12800000,10310000),
  lat = c(42.8920642,36.4919735,31.5036293,46.9952411,40.1998549,32.6023617),
  lng = c(-76.003418,-119.7070313,-99.0966797,-120.6079102,-89.5001221,-83.2983398),
  # NY 42.8920642,-76.003418
  # CA 36.4919735,-119.7070313
  # TX 31.5036293,-99.0966797
  # WA 46.9952411,-120.6079102
  # IL 40.1998549,-89.5001221
  # GA 32.6023617,-83.2983398
  PeopleSickPercentage = c(runif(6))*10)
  PopulationSick <- round(c(StatesHealth$Population*StatesHealth$PeopleSickPercentage/100),0)
  StatesHealth$PopulationSick <- PopulationSick
  TotalPopulation <- sum(StatesHealth$Population)
  
```

### Assign sickness indicator

Assign colors depending on the population that is sicke on each city, Red for more than or equal to 1000000, Yellow for more than or equal to 500000, and Green for less than 500000.


```{r sickness circles, results='hide'}

Red <- 1000000
Yellow <- 500000
Colorfun <- function(PopulationSick){
    if(PopulationSick >= Red) {
      print("Red")
    }
    else {
      if(PopulationSick >= Yellow){
        print("Yellow")
      }
        else {
        print("Green")
        }
    }
}
StatesHealth$ColorOfCircle <- sapply(PopulationSick,"Colorfun")
```

### Results

Table with the data that will be used for the map.

```{r Final table}

StatesHealth
```

## Map - Where to focus the healthcare program
Assessment for the states of California, Georgia, Illinois, New York, Texas, and Washington

#### Date - `r Sys.Date()`

```{r leaflet map, echo=FALSE}
StatesHealth %>%
  leaflet() %>%
    addTiles() %>%
      addCircleMarkers(radius = StatesHealth$PopulationSick/30000 ,color = StatesHealth$ColorOfCircle, popup = paste("State - ",StatesHealth$State,"<br>", "Sick Population - ",StatesHealth$PopulationSick)) %>%
        addLegend(labels = c(" > 1,000,000","< 1,000,000 & > 500,000", "< 500,000"), colors = c("Red","Yellow","Green"))
```